Bricking up and overgrowing backdoors in Intrusion Detection Systems

### 2019-09-08 ex2/paper/paper.tex

\subsection{Performance Results}
Table~\ref{tab:performance_results} shows performance results for both deep learning and random forests. Our results are consistent with previous work like, e.g., \cite{meghdouri_analysis_2018}.

>>>>

\subsection{Performance Results}
Table~\ref{tab:performance_results} shows performance results for both deep learning and random forests, depicting both detection performance of normal samples as contained in the respective datasets and the efficacy of the backdoor. The models are thus able to detect the backdoor with high confidence while retaining high attack detection performance.
Our results are consistent with previous work like, e.g., \cite{meghdouri_analysis_2018}.
